---
title       : "Slidify Project"
subtitle    : "Slidify & Shiny"
author      : "Oscar Reyes"
job         : "DS"
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight  # {highlight.js, prettify, highlight, highlight.js}
hitheme     : solarized_light      #
widgets     : [shiny] # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft, selfcontained}
output: ioslides_presentation
copy_libraries: true
runtime: shiny
logo        : OR.jpg
---
`r opts_chunk$set (echo = FALSE, message = FALSE, comment = "")`

## Server

**_Variables & Description_**

**colm**   : contains the value of selected dataset.                   
**var**    : contains the names of the columns of the selected dataset.   
**dataset**: contains the selected dataset.                             
**graph**  : contains the selected graphic.                            

[Readme File](https://github.com/oreyesc/oreyesc.github.io/blob/master/README.md)

--- 

## Functionality ui.R

In the ui.R the user has tow parts:

**1. Side Bar: has the option to choose:**

  - **Select a dataset**: iris, mtcars or trees.
  
  - **Select density**: from 50 to 250.
  
  - **Select a colour** for the graphs.
  
  - **Select one type of graph**: Bar Plot, Box Plot, Dot Plot, Line Chart, Scatter Plot.
  
**2. mainPanel: has a tabPanel with:**
  - **Dinamyc Information**: shows information (summary or structure) of the selected dataset.

---

## Embedded Code

```{r, echo=FALSE, cache=FALSE, message=FALSE, results='asis', fig.height=5, fig.width=7}
library(ggplot2)
qplot(Height, Girth, data=trees) 

```
[Shiny Application](https://sigma360.shinyapps.io/shinyproject_coursera/)

--- 

## Interactive Information 
```{r, echo=FALSE, cache=FALSE, message=FALSE, results='asis'}
slidifyUI (
        sidebarPanel (
                selectInput ('dataset',
                             'Choose Dataset',
                             c ('iris', 
                                'mtcars',
                                'trees'
                                )
                ),              
                
                selectInput ('type',
                             'Choose Type',
                             c("Summary",
                               "Structure"
                                )
                )
        ),
        mainPanel (
                #tags$div (id = "imageplot",
                #          class = "shiny-html-output imageplot Chart"),
                #tags$p ("text de prueba")
                #tags$table(id = "sumstr", class = "classsum")
                #tags$div (id = "sumstr", class = "shiny-html-output sumstr")
                verbatimTextOutput ("sumstr")
        )
)
#inputPanel (
#        selectInput ("dataset",
#                     label = "Select Data Set:",
#                     choices = c ("mtcars",
#                                  "trees",
#                                  "iris"),
#                     selected = "mtcars"
#        ),
#                
#        selectInput ("variable",
#                     label = "Option: ",
#             choices = c ("Structure",
#                  "Summary","names"),
#             selected = "Structure"
#        ),
#        uiOutput ('a')
#)

#renderDataTable ({
#if (input$dataset == "mtcars") {
#        datainfo <- as.data.frame (mtcars)
#}
#else {
#        if (input$dataset == "trees") {
#                datainfo <- as.data.frame (trees)
#        }
#        else {
#                datainfo <- as.data.frame (iris)
#        }
#}
                
#if (input$variable == "Structure") {
#        output <- str (datainfo)
#}
#else {
#        if (input$variable == "Summary") {
#                output <- summary (datainfo)
#        }
#        else {
#                output <- names(datainfo)
#        }
#}        
#})

```
