---
title       : Slidify Project
subtitle    : Slidify & Shiny
author      : Oscar Reyes
job         : DS
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      #
widgets     : [bootstrap, shiny, interactive] # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
logo        : /OR.jpg
ext_widgets : {rCharts: [libraries/nvd3]}
runtime     : shiny
assets      : {js: 'test.js'}
---

## Description

Application requirements:

1. Some form of input (widget: textbox, radio button, checkbox, ...)
2. Some operation on the ui input in sever.R
3. Some reactive output displayed as a result of server calculations
4. You must also include enough documentation so that a novice user could use your application.
5. The documentation should be at the Shiny website itself.


## Components

<table>
        <tr>
        <td><b>Component</b></td>
        <td><b>Description</b></td>
        </tr>
        <tr>
        <td>ui.R</td>
        <td>user-interface definition of a Shiny web application.</td>
        </tr>
        <tr>
        <td>server.R</td>
        <td>logic for a Shiny web application</td>
        </tr>
        </table>


--- &twocol

## Functionality ui.R

*** =left
In the ui.R the user has tow parts:

**1. Side Bar: has the option to choose:**

  - **Select a dataset**: iris, mtcars or trees.
  - **Select two variables**: X and Y variables.
  - **Select density**: from 50 to 250.
  - **Select a colour** for the graphs.
  - **Select one type of graph**:
    - Bar Plot.
    - Box Plot.
    - Dot Plot.
    - Line Chart.
    - Scatter Plot.

*** =right
**2. mainPanel: has a tabPanel with:**
  - **Dinamyc Plot**: shows the selected graphic created with the information of the selected dataset.
  - **Structure**: shows the selected dataset structure.
  - **Summary**: shows the selected dataset summary.
  - **Data**: shows the dataof the X variable.


---

## Server and Libraries
In the server.R are:

<table>
        <tr>
                <td>**Variable**</td>
                <td>**Functionality**</td>
        </tr>
        <tr>
                <td>colm</td>
                <td>contains the value of selected dataset</td>
        </tr>
        <tr>
                <td>var</td>
                <td>contains the names of the columns of the selected dataset.</td>
        </tr>
        <tr>
                <td>dataset</td>
                <td>contains the selected dataset.</td>
        </tr>
        <tr>
                <td>graph</td>
                <td>contains the selected graphic.</td>
        </tr>
</table>

### Libraries:

`shiny` , `ggplot`, `car`, `RcppEigen`


--- .class #id

## Embedded Code

```{r md-cars-scatter, message=FALSE, fig.width=7, fig.height=5}
library(ggplot2)
qplot(hp, mpg, data=mtcars)+geom_smooth()
```
[Shiny Application](https://sigma360.shinyapps.io/shinyproject_coursera/)


--- .class #id

## Interactive Information 
```{r opts.label = 'shiny'}
slidifyUI (
        sidebarPanel (
                selectInput ('dataset',
                             'Choose Dataset',
                             c ('iris', 
                                'mtcars',
                                'trees'
                                )
                ),              
                
                selectInput ('type',
                             'Choose Type',
                             c("Summary",
                               "Structure"
                                )
                )
        ),
        mainPanel (
                #tags$div (id = "imageplot",
                #          class = "shiny-html-output imageplot Chart"),
                #tags$p ("text de prueba")
                #tags$table(id = "sumstr", class = "classsum")
                #tags$div (id = "sumstr", class = "shiny-html-output sumstr")
                verbatimTextOutput ("sumstr")
        )
)
```


--- &interactive

## Interactive Chart 
```{r echo = F, results = 'asis'}
require (rCharts)
cardata <- as.data.frame (mtcars)
printdata <- nPlot (mpg ~ hp,
                    group = 'carb',
                    type = 'multiBarChart',
                    data = subset (cardata, mpg >=10)
                   )
printdata$print ('chart1')
```
