---
title       : "Slidify Project"
subtitle    : "Slidify & Shiny"
author      : "Oscar Reyes"
job         : "DS"
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight  # {highlight.js, prettify, highlight, highlight.js}
hitheme     : solarized_light      #
widgets     : [bootstrap, shiny, interactive] # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft, selfcontained}
output: ioslides_presentation
runtime: shiny
logo        : OR.jpg
---
<style>
slide.smallcode pre {
  font-size: 15px;
}
pre {
  font-size: 15px;
}
.header {

font-family: Arial, Helvetica, sans-serif;

font-size: 24px;

font-weight: bold;

color: #FFFFFF;

background-color: #000000;

background-position: center top;

height: 50px;

width: auto;

text-align: center;

}

.body {

font-family: Arial, Helvetica, sans-serif;

font-size: 14px;

background-color: #000000;

float: none;

height: 107px;

width: 630px;

line-height: 25px;

margin-right: 126px;

}
/* Fonts and Spacing */
article p, article li, article li.build, section p, section li{
  font-family: 'Open Sans','Helvetica', 'Crimson Text', 'Garamond',  'Palatino', sans-serif;
  text-align: justify;
  font-size:22px;
  line-height: 1.5em;
  color: #AA7139;
}
/* Reduce Space between Title and Body */
slides > slide > hgroup + article {
  margin-top: 15px;
}
</style>
## Server

| Variable |                        Functionality                       |
| :------: | :--------------------------------------------------------: |
|   colm   | contains the value of selected dataset.                    |
|   var    | contains the names of the columns of the selected dataset. |
|  dataset | contains the selected dataset.                             |
|   graph  | contains the selected graphic.                             |

:-------:
--- 

## Functionality ui.R

In the ui.R the user has tow parts:

**1. Side Bar: has the option to choose:**

  - **Select a dataset**: iris, mtcars or trees.
  
  - **Select density**: from 50 to 250.
  
  - **Select a colour** for the graphs.
  
  - **Select one type of graph**: Bar Plot, Box Plot, Dot Plot, Line Chart, Scatter Plot.
  
**2. mainPanel: has a tabPanel with:**
  - **Dinamyc Information**: shows information (summary or structure) of the selected dataset.
---

## Embedded Code

```{r md-trees-scatter, message=FALSE,results='asis', fig.height=4, fig.width=6}
library(ggplot2)
qplot(Height, Girth, data=trees) 

```
[Shiny Application](https://sigma360.shinyapps.io/shinyproject_coursera/)
--- 

## Interactive Information 
```{r,echo=FALSE, results='asis',size=1,dpi=1,size='small'}
inputPanel (
        selectInput ("dataset",
                     label = "Select Data Set:",
                     choices = c ("mtcars",
                                  "trees",
                                  "iris"),
                     selected = "mtcars"
        ),
        
        selectInput ("variable",
                     label = "Option: ",
                     choices = c ("Structure",
                                  "Summary","names"),
                     selected = "Structure"
        )        
)

renderPrint ({
        if (input$dataset == "mtcars") {
                datainfo <- as.data.frame (mtcars)
        }
        else {
                if (input$dataset == "trees") {
                        datainfo <- as.data.frame (trees)
                }
                else {
                        datainfo <- as.data.frame (iris)
                }
        }
        
        if (input$variable == "Structure") {
                str (datainfo)
        }
        else {
                if (input$variable == "Summary") {
                        summary (datainfo)
                }
                else {
                        names(datainfo)
                }
        }        
})
```
